Rare-event sampling applied to the simulation of extreme mechanical efforts exerted by a turbulent flow on a bluff body

### 2019-08-27 draft_p2.tex
Take out bold font for Freddy's part on return times

{\bf The waiting times $\tau$ are defined as the time between two consecutive occurrences of peak fluctuations with amplitude $f_d \geq a$, as illustrated in Fig.~\ref{fig:illustrate_return_time}.  The mixing time $\tau_m$ is the time needed for the dynamics to loose the memory of its initial conditions. As soon as the typical waiting times are much larger than the mixing time $\tau_m$, the occurrences of such events follow a Poisson process and the distribution of the waiting times is exponential: $P(\tau)=\lambda(a)\exp(-\lambda(a)\tau)$, where $r(a)=1/\lambda(a)$ is the average waiting time \cite{lestang_computing_2018}. $r(a)$ is called the {\it return time} of the level $a$. For systems without multistability, it is often the case that the mixing time $\tau_m$ is of the order of the correlation time $\tau_c$.

@@

The shape of the return time $r$ as a function of the return level $a$ is system dependent. It is often the case that  $r(a) = t(a)/\mathbb{P}(f_d\geq a)$, where the level dependent time scale $t(a)$, expected to be of order $\tau_c$, changes much more slowly with $a$ that the PDF ${\mathbb{P}(f_d\geq a)}$, for large values of $a$. As the PDF ${\mathbb{P}(f_d\geq a)}$ was shown to be well approximated by an exponential (see figure Fig.~\ref{fig:pdf_drag}), we might expect that 
\begin{equation}
 \label{eq:return_time}
r(a) \underset{a\to\infty}{\propto} \exp(-la)
\end{equation}
where $l$ is the rate describing the positive tail of the \ac{pdf} of the drag (shown in Fig.~\ref{fig:pdf_drag}).
Fig.~\ref{fig:return_time_instant} shows the evolution of the return time $r(a)$ with the amplitude of fluctuation $a$, computed from {direct sampling} of the drag signal $f_d(t)$ \cite{lestang_computing_2018}. It is consistently found that the return time $r(a)$ is well approximated by an exponential for large levels $a$. Let us also point out some deviation from the exponential law at the largest levels, that are probably the consequence of undersampling.
}
% typically for $a \gtrsim 8 \sigma$ with $\sigma$ being the standard deviation.

>>>>

The waiting times $\tau$ are defined as the time between two consecutive occurrences of peak fluctuations with amplitude $f_d \geq a$, as illustrated in Fig.~\ref{fig:illustrate_return_time}.  The mixing time $\tau_m$ is the time needed for the dynamics to loose the memory of its initial conditions. As soon as the typical waiting times are much larger than the mixing time $\tau_m$, the occurrences of such events follow a Poisson process and the distribution of the waiting times is exponential: $P(\tau)=\lambda(a)\exp(-\lambda(a)\tau)$, where $r(a)=1/\lambda(a)$ is the average waiting time \cite{lestang_computing_2018}. $r(a)$ is called the {\it return time} of the level $a$. For systems without multistability, it is often the case that the mixing time $\tau_m$ is of the order of the correlation time $\tau_c$.

@@

The shape of the return time $r$ as a function of the return level $a$ is system dependent. It is often the case that  $r(a) = t(a)/\mathbb{P}(f_d\geq a)$, where the level dependent time scale $t(a)$, expected to be of order $\tau_c$, changes much more slowly with $a$ that the PDF ${\mathbb{P}(f_d\geq a)}$, for large values of $a$. As the PDF ${\mathbb{P}(f_d\geq a)}$ was shown to be well approximated by an exponential (see figure Fig.~\ref{fig:pdf_drag}), we might expect that 
\begin{equation}
 \label{eq:return_time}
r(a) \underset{a\to\infty}{\propto} \exp(-la)
\end{equation}
where $l$ is the rate describing the positive tail of the \ac{pdf} of the drag (shown in Fig.~\ref{fig:pdf_drag}).
Fig.~\ref{fig:return_time_instant} shows the evolution of the return time $r(a)$ with the amplitude of fluctuation $a$, computed from {direct sampling} of the drag signal $f_d(t)$ \cite{lestang_computing_2018}. It is consistently found that the return time $r(a)$ is well approximated by an exponential for large levels $a$. Let us also point out some deviation from the exponential law at the largest levels, that are probably the consequence of undersampling.

% typically for $a \gtrsim 8 \sigma$ with $\sigma$ being the standard deviation.
